Research Notes

### 2018-11-12 writeups/notes.tex
typo
check in new notes, sync

For our stratified atmosphere problem, $\omega^2 = \frac{N^2 k_x^2}{k^2 +
\frac{1}{4H^2}}$. This corresponds to $\vec{v}_{ph} = \frac{Nk_x}{\sqrt{k_x^2 +
k_z^2 + 1/4H^2}} \vec{k}$.

@@

Edit: Looks like Bhagat 2018 J.\ Fluid.\ Mech.\ does this more correctly, they
find that surface tension is the proper term to invoke after performing this
boundary layer analysis. I'm not going to finish reworking the rest of Bohr's
paper here, since it's up through the boundary layer equations that is reusable.
\end{document}

>>>>

For our stratified atmosphere problem, $\omega^2 = \frac{N^2 k_x^2}{k^2 +
\frac{1}{4H^2}}$. This corresponds to $\vec{v}_{ph} = \frac{Nk_x}{\p*{k_x^2 +
k_z^2 + 1/4H^2}^{3/2}} \vec{k}$.

@@

Edit: Looks like Bhagat 2018 J.\ Fluid.\ Mech.\ does this more correctly, they
find that surface tension is the proper term to invoke after performing this
boundary layer analysis. I'm not going to finish reworking the rest of Bohr's
paper here, since it's up through the boundary layer equations that is reusable.

\section{Paper Notes}

\begin{itemize}
    \item \emph{Lindzen 1968} A Theory of the QBO\@: IGW are excited from below
        with a distribution of phase velocities $c \in \s*{-c_0, c_0}$. Then, if
        you allow a shear layer to absorb a particular phase velocity, the mean
        flow will propate downwards until it creates a discontinuity (because
        there's no more inbound IGW at the correct $c > c_0$). Then, once the
        ledge leaves the driveable zone, perhaps the flow flips (very roughly).

        Note that follow-up paper Holton \& Lindzen 1972 attributes the mean
        flow deposition to radiative cooling instead of critical layer
        absorption, TODO investigate.

    \item \emph{Jones 1970} Coupling IGW mean flow: numerical study: as IGW
        steepens shelf, more transmission than linear steady state theory.

    \item \emph{Couson \& Lecoanet 2018} Slowly-reversing Mean Flows: Convection
        drives spectrum of waves that become IGW at transition, produces QBOs.

        Key note: momentum deposition by viscous dissipation dominates critical
        layer absorption in the WKB model?
\end{itemize}
\end{document}
